On existence of integral point sets and their diameter bounds \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2019-11-30 pps-linear-bound/pps-linear-lower-bound.tex
[J220] Fix misprints

\section{Collinear subsets of integral point sets}
Integral point sets with many collinear ponts are very dominating examples.
In this section we estimate the cardinality of an intersection of an integral point set with a line segment.

@@

\begin{proof}
	Let $f(k)$ denote the mininal length of a line segment
	that intersects an integral point set by $k$ points.
	We observe that $f(k) > f (k-1)$.
	Due to Lemma~\ref{lem:line_segment_with n_squared_plus_one_points},
	$f(n^2+1) \geq \frac{2}{3}n^3+\frac{1}{2}n^2-\frac{1}{6}n$.

@@

In~\cite{kurz2008bounds}, thorough investigation of planar integral point sets with diameter at most 10 000
is carried out;
thus, we can restrict our attention to intersections of planar integral point sets with lne segments of length more than 10 000.

>>>>

\section{Collinear subsets of integral point sets}
Integral point sets with many collinear points are very dominating examples.
In this section we estimate the cardinality of an intersection of an integral point set with a line segment.

@@

\begin{proof}
	Let $f(k)$ denote the minimal length of a line segment
	that intersects an integral point set by $k$ points.
	We observe that $f(k) > f (k-1)$.
	Due to Lemma~\ref{lem:line_segment_with n_squared_plus_one_points},
	$f(n^2+1) \geq \frac{2}{3}n^3+\frac{1}{2}n^2-\frac{1}{6}n$.

@@

In~\cite{kurz2008bounds}, thorough investigation of planar integral point sets with diameter at most 10~000
is carried out;
thus, we can restrict our attention to intersections of planar integral point sets with line segments of length more than 10~000.
